\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1cm,bottom=1cm}

\ifxetexorluatex
  \setmainfont{Times New Roman}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{mathptmx}
\fi

\usepackage[hidelinks]{hyperref}

\definecolor{Black}{HTML}{000000}
\colorlet{heading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

% Compact section command
\renewcommand{\cvsection}[2][]{%
  \bigskip%
  {\color{heading}\large\bfseries\MakeUppercase{#2}}\\[-1ex]%
  {\color{heading}\rule{\linewidth}{0.5pt}\par}\medskip
}

% Compact job entry: Company - Role - Dates - Description
\newcommand{\cvjob}[4]{%
  \textbf{#1} {\small(#4)} -- \textit{#2} \hfill {\small #3}\par\smallskip
}

% Sub-entry under a company: Team - Description - Dates
\newcommand{\cvsubentry}[3]{%
  \hspace{0.5em}\textit{#1} {\small(#2)} \hfill {\small #3}\par\smallskip
}

% Compact education entry: Degree - Institution - Dates
\newcommand{\cvedu}[3]{%
  #1 -- \textit{#2} \hfill {\small #3}\par\smallskip
}

\begin{document}

\name{JAVIER RODRÍGUEZ}
\tagline{Backend Developer}
\personalinfo{
\faEnvelope\hspace{0.3em}\href{mailto:javierrd96@gmail.com}{javierrd96@gmail.com}\quad
\faPhone\hspace{0.3em}+61 451 494 198\quad
\faGlobe\hspace{0.3em}\href{https://javi.dev}{javi.dev}\quad
\faGithub\hspace{0.3em}\href{https://github.com/zhonskate}{github.com/zhonskate}\quad
\faLinkedin\hspace{0.3em}\href{https://www.linkedin.com/in/zhonskate}{linkedin.com/in/zhonskate}
}

\makecvheader

\cvsection{Summary}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item 7+ years building reliable, scalable Backend Python services. Shipped production APIs and integrations across fintech and SaaS.
\item Co-founder with end-to-end product ownership from discovery to GTM; now in maintenance only and seeking a full-time role.
\item Worked across publicly and privately funded organizations, contributing to teams both onsite and remotely.
\end{itemize}
}

\cvsection{Education}
\cvedu{\textbf{Master's in Cloud and HPC} (Cloud specialization)}{Universitat Politècnica de València}{Sep 2018 - Dec 2020}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Special mention (top 3 out of 50+ students) in Cloud Computing \& Grid Computing courses.
\item Master's thesis Serverless computing, exploring the concept of Functions as a Service (FaaS) and their use cases. Grade: 8,5/10.
\end{itemize}
}\medskip
\cvedu{\textbf{Bachelor's in Computer Science} (Computing specialization)}{Universitat Politècnica de València}{Sep 2014 - Jul 2018}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Special mention (top 3 out of 400+ students) in Programming I, Automata Theory \& Introduction to Computer Graphics courses.
\item Second place in the Cajamar UniversityHack Datathon 2018 - Salesforce predictive modelling challenge, a Spain-wide competition.
\item Bachelor's thesis on extending Jupyter for distributed, collaborative use. Explored the concept of kernels and variable context. Grade: 9,8/10.
\end{itemize}
}\medskip
\cvedu{\textbf{AWS Certified Solutions Architect}}{Amazon Web Services}{Mar 2024}

\cvsection{Skills}
{\small
\begin{minipage}[t]{0.48\linewidth}
\textbf{Programming:} Python, JavaScript, TypeScript, SQL, Bash\\
\textbf{Backend:} FastAPI, PostgreSQL, SQLAlchemy, Django, Flask \\
\textbf{Frontend:} HTMX, Svelte, Vue, Tailwind CSS\\
\textbf{AI:} AI Agents, LLMs, Claude code, Cursor, Langchain\\
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Terraform, CI/CD\\
\textbf{Tools:} Linux, Git, Jupyter, LaTeX, Ledger-CLI\\
\textbf{Monitoring:} Sentry, Mixpanel, Datadog, Intercom\\
\textbf{Languages:} English (fluent), Spanish \& Catalan (native)\\
\end{minipage}
}

\cvsection{Work Experience}

\cvjob{Cordada}{Co-Founder}{Sep 2024 - Jan 2026}{Spanish-based startup}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Built \href{https://enrutar.com}{enrutar.com}, an operations SaaS for trades businesses, leading product and engineering.
\item Delivered multi-tenant backend with FastAPI/PostgreSQL on Hetzner; S3 storage, Stripe billing, Mixpanel, background jobs with Celery, RBAC, notifications, and observability; Programmed frontend in Svelte, and Tailwind CSS, leveraging AI tools as Claude code and Cursor.
\item Owned GTM: customer discovery and, paid/organic acquisition, and support. €400 MRR with 10 paying accounts.
\end{itemize}
}\medskip

\cvjob{Gangverk}{Backend Developer}{}{Leading Icelandic software consulting agency}

\cvsubentry{PayAnalytics team}{Icelandic salary management SaaS}{May 2024 - Sep 2024}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Automated migration of 5,000+ GitHub issues to Jira with full fidelity, conserving data integrity; zero-downtime cutover.
\item Contributed to internal customer panel APIs and permissions, participating in their an audit tool development.
\end{itemize}
}\smallskip

\cvsubentry{Kvika team}{Icelandic investment and commercial bank}{Apr 2021 - May 2024}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Built and maintained backend services for Kvika website and Auður banking app (25k+ users); integrated with icelandiccore banking systems.
\item Rebuilt customer onboarding flows (KYC, appropriateness), enabling new products and reducing drop-off rate by 30\%.
\item Implemented portfolio tracking backend ingesting, transforming and serving historical market data; established idempotent pipelines and tests.
\end{itemize}
}\medskip

\cvjob{ITI - Instituto Tecnológico de Informática}{R\&D Technician}{Mar 2018 - Apr 2021}{Spanish public R\&D institute}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Developed distributed services across AI, big data, and blockchain; contributed to European publicly funded projects (RADIATUS).
\item Explored and gave presentations on different technologies and tools, such as Docker, data consistency models, and database sharding.
\item Participated in the design and architectureof a nation-wide medical record system, dealing with computing, privacy and security requirements.
\end{itemize}
}\medskip

\cvjob{Diebold Nixdorf}{Remote Assistance Technician - Intern}{Sep 2017 - Feb 2018}{ATM and banking technology}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Automated Linux server maintenance and document recovery using bash and shell scripts; reduced manual effort by 50\%.
\item Communicated in real time with customers via remote desktop and phone, providing technical support and troubleshooting.
\end{itemize}
}

\cvsection{Interests}
{\small 
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Film photography: I've been taking film photos and collecting film cameras for the past 6 years.
\item Adventure sports: I love to go hiking, rock climbing and snowboarding. I'm also a PADI advanced open water diver.
\item Birdwatching: I recently picked up birdwatching as a hobby and I'm enjoying greatly the Australian wildlife.
\end{itemize}
}

\end{document}
