\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=1.25cm,right=1.25cm,top=1cm,bottom=1cm}

\ifxetexorluatex
  \setmainfont{Times New Roman}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{mathptmx}
\fi

\usepackage[hidelinks]{hyperref}

\definecolor{Black}{HTML}{000000}
\colorlet{heading}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

% Compact section command
\renewcommand{\cvsection}[2][]{%
  \bigskip%
  {\color{heading}\large\bfseries\MakeUppercase{#2}}\\[-1ex]%
  {\color{heading}\rule{\linewidth}{0.5pt}\par}\medskip
}

% Compact job entry: Company - Role - Dates - Description
\newcommand{\cvjob}[4]{%
  \textbf{#1} {\small(#4)} -- \textit{#2} \hfill {\small #3}\par\smallskip
}

% Sub-entry under a company: Team - Description - Dates
\newcommand{\cvsubentry}[3]{%
  \hspace{0.5em}\textit{#1} {\small(#2)} \hfill {\small #3}\par\smallskip
}

% Compact education entry: Degree - Institution - Dates
\newcommand{\cvedu}[3]{%
  #1 -- \textit{#2} \hfill {\small #3}\par\smallskip
}

\begin{document}

\name{JAVIER RODRÍGUEZ}
\tagline{Senior Python Developer}
\personalinfo{
\faEnvelope\hspace{0.3em}\href{mailto:javierrd96@gmail.com}{javierrd96@gmail.com}\quad
\faPhone\hspace{0.3em}+61 451 494 198\quad
\faGlobe\hspace{0.3em}\href{https://javi.dev}{javi.dev}\quad
\faGithub\hspace{0.3em}\href{https://github.com/zhonskate}{github.com/zhonskate}\quad
\faLinkedin\hspace{0.3em}\href{https://www.linkedin.com/in/zhonskate}{linkedin.com/in/zhonskate}
}

\makecvheader

\cvsection{Summary}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item 7+ years building reliable, scalable Python services with Django and FastAPI. Shipped production APIs and integrations across fintech, SaaS, and government-funded projects.
\item Security-conscious developer with experience in regulated environments (banking, public R\&D); strong focus on code reviews, automated testing, and documentation.
\item Effective stakeholder communicator across public and private organizations; experienced working onsite and remotely in small, collaborative teams.
\end{itemize}
}

\cvsection{Education}
\cvedu{\textbf{Master's in Cloud and HPC} (Cloud specialization)}{Universitat Politècnica de València}{Sep 2018 - Dec 2020}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Special mention (top 3 out of 50+ students) in Cloud Computing \& Grid Computing courses.
\item Master's thesis Serverless computing, exploring the concept of Functions as a Service (FaaS) and their use cases. Grade: 8,5/10.
\end{itemize}
}\medskip
\cvedu{\textbf{Bachelor's in Computer Science} (Computing specialization)}{Universitat Politècnica de València}{Sep 2014 - Jul 2018}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Special mention (top 3 out of 400+ students) in Programming I, Automata Theory \& Introduction to Computer Graphics courses.
\item Second place in the Cajamar UniversityHack Datathon 2018 - Salesforce predictive modelling challenge, a Spain-wide competition.
\item Bachelor's thesis on extending Jupyter for distributed, collaborative use. Explored the concept of kernels and variable context. Grade: 9,8/10.
\end{itemize}
}\medskip
\cvedu{\textbf{AWS Certified Solutions Architect}}{Amazon Web Services}{Mar 2024}

\cvsection{Skills}
{\small
\begin{minipage}[t]{0.48\linewidth}
\textbf{Programming:} Python, JavaScript, TypeScript, SQL, Bash\\
\textbf{Backend:} Django, FastAPI, Flask, PostgreSQL, SQLAlchemy \\
\textbf{Frontend:} Svelte, HTMX, Vue, Tailwind CSS\\
\textbf{Testing \& QA:} Pytest, automated testing, code reviews, CI/CD\\
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\linewidth}
\textbf{Cloud \& DevOps:} AWS, Docker, Kubernetes, Terraform, CI/CD\\
\textbf{Tools:} Linux, Git, Jupyter, LaTeX, Ledger-CLI\\
\textbf{Monitoring:} Sentry, Mixpanel, Datadog, Intercom\\
\textbf{Languages:} English (fluent), Spanish \& Catalan (native)\\
\end{minipage}
}

\cvsection{Work Experience}

\cvjob{Cordada}{Co-Founder}{Sep 2024 - Jan 2026}{Spanish-based startup}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Built \href{https://enrutar.com}{enrutar.com}, an operations SaaS for trades businesses, leading product and engineering.
\item Delivered multi-tenant backend with FastAPI/PostgreSQL; implemented RBAC, secure authentication, S3 storage, Stripe billing, background jobs with Celery, and observability. Programmed JavaScript frontend in Svelte and Tailwind CSS.
\item Wrote automated tests, performed code reviews, and documented technical specifications for handover and ongoing support.
\end{itemize}
}\medskip

\cvjob{Gangverk}{Backend Developer}{}{Leading Icelandic software consulting agency}

\cvsubentry{PayAnalytics team}{Icelandic salary management SaaS}{May 2024 - Sep 2024}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Developed and maintained Django APIs for internal customer panel, implementing permissions and access controls for an audit tool.
\item Automated migration of 5,000+ GitHub issues to Jira with full fidelity, conserving data integrity; zero-downtime cutover.
\end{itemize}
}\smallskip

\cvsubentry{Kvika team}{Icelandic investment and commercial bank}{Apr 2021 - May 2024}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Built and maintained secure Python backend services for Kvika website and Auður banking app (25k+ users); integrated with core banking systems adhering to strict security and compliance standards.
\item Rebuilt customer onboarding flows (KYC, appropriateness) with thorough testing and code reviews, enabling new products and reducing drop-off rate by 30\%.
\item Implemented portfolio tracking backend ingesting, transforming and serving historical market data; established idempotent pipelines, automated tests, and technical documentation.
\end{itemize}
}\medskip

\cvjob{ITI - Instituto Tecnológico de Informática}{R\&D Technician}{Mar 2018 - Apr 2021}{Spanish public R\&D institute}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Developed secure distributed services across AI, big data, and blockchain; contributed to European publicly funded cybersecurity project (RADIATUS).
\item Collaborated with stakeholders to gather requirements and document technical specifications for cloud-based platforms and data systems.
\item Participated in the design and architecture of a nation-wide medical record system, addressing computing, privacy, and security requirements.
\end{itemize}
}\medskip

\cvjob{Diebold Nixdorf}{Remote Assistance Technician - Intern}{Sep 2017 - Feb 2018}{ATM and banking technology}
{\small
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Automated Linux server maintenance and document recovery using bash and shell scripts; reduced manual effort by 50\%.
\item Communicated in real time with customers via remote desktop and phone, providing technical support and troubleshooting.
\end{itemize}
}

\cvsection{Interests}
{\small 
\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=*]
\item Film photography: I've been taking film photos and collecting film cameras for the past 6 years.
\item Adventure sports: I love to go hiking, rock climbing and snowboarding. I'm also a PADI advanced open water diver.
\item Birdwatching: I recently picked up birdwatching as a hobby and I'm enjoying greatly the Australian wildlife.
\end{itemize}
}

\end{document}
